Estimate Response to Selection

### 2022-07-06 R/03-response.Rmd

plot_flux(fluxes, passage, log_ch4, ratio_log10, log10 = TRUE)

#ggsave('fluxes_log.pdf', width = 5, height = 4)
```

@@

```{r save_model}
save(response_model, compare_response_mods, per_slope, file = '../Output/response_model.RData')
```

>>>>

p_response <- plot_flux(fluxes, passage, log_ch4, ratio_log10, log10 = TRUE)

save(p_response, file = 'Output/response_plot.RData')

ggsave('Manuscript/fig1.jpg', p_response, width = 4, height = 3)

@@

```{r save_model}
save(response_model, compare_response_mods, per_slope, file = 'Output/response_model.RData')
```
